Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-04 paper/preprint/appendix.Rmd

>>>>

# Discontinuity Analysis

We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
[table with each child's age of onset per milestone?]

```{r, get-milestones, echo=F}
motor <- read_csv(here::here("data","raw_data", "saycam_walking_asq.csv"))
# A and S are sitting at 6mos
face_hand_by_age_milestones <- face_hand_by_age %>%
  mutate(sit = ifelse(child_id=="S" | child_id=="A", 1, 
                      ifelse(child_id=="Y" & age_day_bin > 8, 1, 0))) %>%
  mutate(cruise = ifelse((child_id=="S" & age_day_bin >= 9) | 
                      (child_id=="A" & age_day_bin >= 10) | 
                      (child_id=="Y" & age_day_bin > 9), 1, 0)) %>%
  mutate(walk = ifelse((child_id=="S" & age_day_bin > 10) |
                       (child_id=="A" & age_day_bin > 13) |
                       (child_id=="Y" & age_day_bin > 16), 1, 0)) %>%
  mutate(age = age_day_bin)

library(lmerTest)
library(sjPlot)
library(sjmisc)
# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
# so we drop random slopes
```

## Sitting

Children's age at which they began sitting did not significantly predict changes in either the amount of faces or hands that they saw.

```{r}
face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(face_sit) # ns
tab_model(face_sit, show.re.var=F, dv.labels = "Proportion of Faces")
```

```{r}
hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(hand_sit) # ns
tab_model(hand_sit, show.re.var=F, dv.labels = "Proportion of Hands")
```

## Cruising

As children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$. 
For faces, there was a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).

```{r}
face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
summary(face_cruise) 
# age+., cruise+*, age*cruise-*
tab_model(face_cruise, show.re.var=F, dv.labels = "Proportion of Faces")
```

```{r, include=F}
# need to also include main effect terms ("age" and "cruise")?
face_cruise_eff <- effects::effect(term="age:cruise", mod=face_cruise)
fc_dat <- data.frame(face_cruise_eff) %>% filter(cruise==0 | cruise==1)
fc_dat %>% ggplot(aes(x=age, y=fit, group=cruise, color=cruise)) +
  geom_line() +
  geom_ribbon(aes(x=age, ymin=lower, ymax=upper, fill=cruise), alpha= 0.3) +
  geom_point(data=face_hand_by_age_milestones, aes(x=age, y=prop_faces))
```

```{r}
hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
summary(hand_cruise) 
# cruise+*, age*cruise-.
tab_model(hand_cruise, show.re.var=F, dv.labels = "Proportion of Hands") # show.obs=F
```

## Walking

As children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).

```{r}
face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
#summary(face_walk) # ns
tab_model(face_walk, show.re.var=F, dv.labels = "Proportion of Faces")
```

```{r}
hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
#summary(hand_walk) # walk+.
tab_model(hand_walk, show.re.var=F, dv.labels = "Proportion of Hands")
```
